---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Before analysing, we need to laod the data into an R dataframe. It is assumed that the data lies in a zip file within the same directory as this .Rmd file.

```{r}
activity_data <- read.table(unz("activity.zip", "activity.csv"), header=TRUE, sep = ",", na.string="NA")

```
Let's have some closer look at the data.
```{r}
nrow(activity_data)
str(activity_data)
head(activity_data)
tail(activity_data)
summary(activity_data)
```
So, this data set contains 17568 entries with 2304 missing values in the activity column. The data was measured in the months October and November in 2012 every 5 minutes, with each day having 288 entries.

## What is mean total number of steps taken per day?

```{r}
grouped_activity_data <- group_by(activity_data, date)
steps_per_day <- summarize(grouped_activity_data, sum_steps = sum(steps, na.rm=TRUE))
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
